README.Rmd

### 2018-11-22 manuscripts/manuscript.Rmd
minor edits on 2nd review

The challenge of making decisions under uncertainty is obviously not unique to fisheries. Existing methods we optimal control methods which similarly assume perfect measurements can be found in a wide range of population and ecosystem management challenges, including fire ecology [@Richards1999], invasive species [@Blackwood2010; @Shea1998], disease outbreaks [@Shea2014; @Li2017], and protecting biodiversity [@Dee2017; @Iacona2017], and in common textbooks and reviews [@Mangel1985; @Clark1990; @Marescot2013].  Yet fisheries conservation and management has long been both a crucible and proving ground for the theory of ecological management more generally, including topics such as adaptive management [@Walters1978], ecosystem-based management [@Levin2008] and resilience thinking [@Holling1973; @May1977], while also giving rise to the sub-discipline of resource economics [@Beverton1957; @Schaefer1954; @Gordon1954], thanks to its global relevance, long history, and readily available data.  Despite the generality of the models and issue of measurement uncertainty considered here, any application must be grounded in both the history and context of the particular decision problem. In light of this, we begin with a brief background on existing decision theory approaches common in fisheries management.

In this paper, we examine three strategies to managing a natural population, such as a fishery, under such uncertainty.  This problem has a long history in both theory and practice, where seemingly innocuous simplifying assumptions have led to a deep paradox in how managers should respond to uncertainty.  The precautionary principle [@Kriebel2001] would seem to suggest that the greater the uncertainty in our models, the more cautious we should be in management policies.  Yet a well-known mathematical proof by @Reed1979 established that under quite general conditions, the optimal strategy under uncertainty is no different than under no uncertainty at all.  Attempts to resolve this have since only deepened this paradox, arguing that adding additional sources of uncertainty, such as imperfect measurements, should lead to optimal harvest that increases with greater uncertainty [e.g. @Clark1986; @Sethi2005].  Meanwhile, much of actual practice has (perhaps fortunately, as we shall see) ignored these results in favor of a more heuristic application of the precautionary principle.  Here, we show that this paradox can be resolved by uncovering previous shortcuts and tackling the optimal management problem head-on, which we can solve thanks to the computational efficiency of sophisticated algorithms developed more recently in the field of robotics.  This approach allows us to reject this paradox largely in favor of the precautionary principle. Further, our comparisons show that widely recognized existing approaches in both theory and practice are not by themselves sufficient to manage a population under substantial uncertainty over the long term, but our recently borrowed approach from robotics literature can under identical conditions sustain both higher biomass and higher economic yields than those approaches.  This conclusion has important implications not only for fisheries but ecosystem more broadly: underscoring the danger of not correctly accounting for measurement uncertainty when making decisions, and further to the significant opportunity to learn from fields such as robotics when faced with complex and uncertain decisions.

@@

where the $\min$ function ensures no additional reward for attempting to harvest more than the entire stock.  In economic terms, the corresponds to a fixed price per fish caught, with no proportional cost on effort required to do so, but the results do not depend on this assumption, as existing analyses have previously established [@Reed1979].  Using this form allows a more direct comparison to approaches such as maximum sustainable yield (MSY) which do not include an economic model but merely maximize long-term catch. In principle, utility could also reflect ecosystem services or other intrinsic values for fish left in the sea and not merely the market for consumption [@Halpern2013].

The solution to this decision problem is conditional on a population model for the underlying ecological process, describing probability the system moves to state $x_{t+1}$ given that it was in state $x_t$ and the manager selected a harvest $h_t$, which we discuss below.  Such a model would typically be estimated and parameterized from available data, often (but not necessarily) using a hierarchical Bayesian approach that acknowledges the existence of uncertainty in both measurements and process [e.g. see @Dichmont2016 for a discussion of how uncertainties are frequently included in stock assessment models].  However, accounting for measurement uncertainty when going from data to model does not mean we have also accounted for this uncertainty when going from model to decision.  For example, a harvest decision policy based upon maximum sustainable yield simply depends on the stock size which maximizes the expected growth rate of the model.  Measurement uncertainty in model estimation can indeed influence the position of that maximum, but as we shall see, that strategy is only optimal in the absence of any uncertainty.

There is one further subtlety arising in this seemingly simple problem statement that we must address. Given our discrete-time formulation of the recruitment process, it is necessary to decide if the measurement $y_t$ happens before or after harvest $h_t$: that is do we: measure, recruit, harvest, or measure, harvest, recruit?  Following convention in the optimal control literature (e.g. [@Reed1979; @Clark1990; @Sethi2005]), we will assume the latter; measurement occurs immediately before harvest, followed by recruitment. This assumption has occasionally been reversed to introduce some additional uncertainty from stochastic recruitment immediately prior to setting the harvest quota [e.g. @Clark1986; @Weitzman2002], which appears to mimic uncertainty in measurements but does not allow uncertainty to accumulate since the measurement step still occurs without error.

@@

@Gordon1954 and @Schaefer1954 independently showed in the same year that the maximum sustainable yield for the model bearing their names is achieved by reducing the stock to the  population to the size at which it obtains the maximum growth rate which is known as Biomass at Maximum Sustainable Yield, $B_{MSY}$. For the Gordon-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$.  They observed that fishing at a *constant yield* (that is, an individual fish mortality, $F$, such that harvest $H = F \cdot B$) of $F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}$)  will eventually lead to a population that converges to the biomass $B_{MSY}$ and produces the maximum sustainable harvest, $H_{MSY} = r K / 4$ in this model.  From here, theory and practice diverge.

@@

In the face of a naturally fluctuating population, previous arguments made by @Gordon1954; @Schaefer1954 or @Clark1973 no longer hold.  As noted above, the optimal harvest of a population under a model such as the stochastic Gordon Schaefer, Eq \eqref{Gordon-Schaefer}, is an example of a Markov Decision Problem (MDP) which must be solved with stochastic dynamic programming. Thanks to a mathematical proof provided by @Reed1979, fisheries managers have largely been able to bi-pass such computational effort.  However, this convenient result also opened the door to paradox of uncertainty that would haunt ecological management for at least the next four decades.

@@

Algorithmic innovations from the robotics community have now made it possible to numerically solve non-trivial POMDP problems. The need to consider all past observations becomes particularly demanding given the forward-looking nature of a decision problem.  Not only must we consider all possible sequences of future actions over all possible sequences of future states, but we must add to that all possible sequences of future measurements. The computational complexity involved has historically limited POMDP applications to contexts with only a handful of possible states and actions [e.g. @Chades2008; @Chades2011; @Fackler2014; @Fackler2014b], insufficient to capture fisheries models appropriately.  Meanwhile, methods to solve decision problems with imperfect information have advanced steadily in the field of robotics and artificial intelligence.  Almost contemporaneous with Reed's work,  papers by @Smallwood1973 and @Sondik1978 laid mathematical foundations for algorithms that could efficiently solve POMDP problems [e.g. @Kaelbling1998; @Pineau2003].  More recently, driven by demands in areas such as autonomous vehicle decision making, newer point-based approximation algorithms such as SARSOP [@Kurniawati2008] have made it possible to solve POMDPs with 100s of states and actions.  We have adapt this algorithm for application to the fisheries context, and provide an efficient implementation as a preliminary R package [@sarsop-pkg] which can be used to replicate and further explore results presented here. Details of the analysis presented here including annotated code to reproduce and further explore all of the following results is provided in the supplementary material.

Precise definitions of both the (fully observed) MDPs and POMDPs (not to be confused with Markov Process Models and Hidden Markov Process Models -- methods for which estimate the model but do not involve the feedback of any decision process) in an ecological context can be found in @Williams2011, or in classic work from the engineering and robotics community [e.g. @Smallwood1973 and @Sondik1978].  For convenience, we summarize the POMDP definition and common notation here.  The POMDP problem is posed identically to that of the MDP problem, with the addition of an observation process  The POMDP problem for fisheries question considered here can be summarized as follows:

- Transition function (state equation): $T(x_t, x_{t+1}, a_t)$: the probability that a system is in state $x_{t+1}$ at time $t+1$ given that it began in state $x_t$ at time $t$ and the manager took action $a_t$.  In our context, this relationship is given by the Gordon-Schaefer stock recruitment function $f$ with normally distributed growth uncertainty $x_{t+1} \sim \mathcal{N}(f(x_t,a_t), \sigma_g)$, truncated at zero to exclude negative population sizes. The action $a_t$ represents the harvest quota set for the fishery. Attempting to implement a quota the exceeds the true population size results in collapse of the fishery.  As @Clark1986 eloquently argues, assuming that extinction is impossible regardless of fishing intensity would unreasonably bias the decision problem.

@@

fig1_df %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd=1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  facet_wrap(~ sigma_m, labeller = label_bquote(sigma[m] == .(sigma_m))) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

In the absence of either environmental noise or measurement error POMDP, CE, and MSY would converge to stock at the $B_{MSY}$, while TAC would maintain the stock at a slightly higher level (see Supplemental material, Figure S1).  The introduction of stochastic growth has a significant negative impact on the TAC strategy, with a mean biomass significantly lower than $B_{MSY}$ (first panel, Figure \ref{sims}; this impact is even more severe for MSY, see Figure S2).  Without measurement error, the CE and POMDP strategies are nearly identical with both approximately maintaining the stock at $B_{MSY}$ despite the significant environmental stochasticity.  As measurement error increases in the subsequent panels, CE and TAC strategies perform increasingly poorly, while the POMDP continues to maintain the average stock close to $B_{MSY}$.  Notably, CE is significantly more impacted by measurement uncertainty than TAC, with CE averaging even lower biomass than TAC under moderate measurement uncertainty.  These results confirm that the precautionary approach represented by the TAC does indeed prove more robust to the problem of measurement error than the optimization solution represented by CE, but is less robust to environmental error. In contrast, the POMDP approach successfully handles both sources of uncertainty, maintaining higher stocks, near $B_{MSY}$ level, and producing the highest yield.

```{r econ, fig.width=7, fig.height=3.5, fig.cap="Expected net present value of the fishery across strategies under increasing levels of measurement error $\\sigma_m$. Net present value is the sum of all future harvests discounted over time and averaged across 100 replicates simulations under each strategy, as shown in Figure \\ref{sims}. The value under constant escapement (CE) is optimal when measurements are perfect but decreases rapidly with increasing measurement error. The more cautious TAC is not economically optimal but largely unimpacted by increasing error, while POMDP attains consistently high economic yield despite the increasing uncertainty. \\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "MSY") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

@@

This pattern in management success in ecological terms (the relatively recovery and maintenance of fish biomass) is also borne out in terms of economic performance. We find the mean net present value (averaging across replicates and discounting future profits by the discount factor $\gamma$) for these same simulations at increasing levels of measurement uncertainty (Figure \ref{econ} ).  As before, environmental stochasticity is set at $\sigma_g = 0.15$.  In the absence of measurement uncertainty, constant escapement (CE) is optimal (as per @Reed1979), while the heuristic caution built into the total allowable catch (TAC) strategy (at 80% MSY) results in a sub-optimal economic yield.  The presence of stochasticity in recruitment ($\sigma_g = 0.15$), also contributes to the reduction in yield under TAC.  Though CE is quite robust to the environmental stochasticity level, this strategy proves very sensitive to increasing measurement error, showing sharp declines in economic value, falling below the TAC economic value at $\sigma_m = 0.15$.    Though the risk of stock collapse does increase with increasing measurement error under TAC (as seen by the mean declines in Figure \ref{sims}), these have little impact on the economic value due to the discount rate.  A smaller discount rate would penalize unlikely but not improbable collapses more, since a significant amount of time is required to realize those rare events.  Supplemental Figure S3 summarizes these economic trends across different noise values $\sigma_g$ and includes comparison to a simple MSY policy.  In contrast to the declining economic performance of CE and the consistently sub-optimal economic yield for TAC, the POMDP strategy continues to generate economic yields at approximately the optimal level (as attained by CE in the absence of measurement error) despite the increasingly uncertain measurements.  This demonstrates that the reduced risk of stock collapse and higher average stock biomass attained by the POMDP strategy in the presence of high measurement error, Figure \ref{sims}) is not the result of a trivial reduction in harvesting under all circumstances, but rather, evidence of a more nuanced strategy that manages to account for the uncertainty in measurement while maintaining a reasonable harvest.

@@

```{r overest, fig.width=4, fig.height=3.5, fig.cap = "Average fish biomass when the POMDP strategy assumes a high level of measurement uncertainty, while simulations reflect perfect measurements.  Despite this overestimation, biomass under POMDP strategy closely tracks the optimal biomass under CE in the absence of measurement error.  \\label{overest}"}
overest_sims %>%
  filter(method != "MSY") %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))  + 
  theme(legend.position = "bottom") 
```

@@

This difference between underestimating and overestimating accounts for the poor performance of the CE solution under large measurement uncertainty, where it over-harvests whenever measurements are too large.  Even though underestimating is equally likely under the measurement uncertainty model, sooner or later a run of "heads", a sequence of overestimations relative to the true stock, can drive stocks to very low levels where the chance of local extinction becomes possible.  It is precisely this asymmetry: that too much over-harvesting leads to an irreversible state of extinction, while too much under-harvesting is always reversible (modulo some lost revenue) that lay behind Clark's original intuition that there was something fishy about Reed's result that $S = D$: that uncertainty required no extra caution.  Constant escapement is particularly susceptible to over-harvesting starting from stock sizes much higher than $B_{MSY}$ since its bang-bang optimal solution attempts to bring stocks back to target level as fast as possible. CE is not so vulnerable to collapse from small stock sizes, since it shuts down all harvests once estimates fall below $B_{MSY}$. Stock collapse under TAC can also be driven by such a string of heads, but is unlikely at high stock sizes since harvest never exceeds $H_{MSY}$.  In both cases, some measurement uncertainty interacts with inherent stochasticity, which provides a continued source of variation to sizes above $B_{MSY}$, where CE strategy is most vulnerable, and below $B_{MSY}$, where TAC is most vulnerable.

@@

Using modern algorithms we have been able to both crack the nut of measurement uncertainty in the optimal management of ecological populations such as marine fisheries, debunking a long-standing paradox created by previous literature which has argued that increased measurement uncertainty should be met with equal or larger harvests [e.g. @Reed1979; @Clark1986; @Sethi2005].  By using powerful algorithms developed first the robotics literature to solve POMDPs [@Kurniawati2008], we have been able to tackle this optimal control problem directly rather than resorting to the simplifying assumptions used in previous work.  Our solution confirms the intuition of the precautionary principle in a quantitatively precise form: under most (but not all) conditions, *greater uncertainty results in smaller optimal harvests*.  Despite frequently proposing smaller harvests than existing approaches, the POMDP solution achieves higher long-term economic value as well as higher average stock sizes over the long term.

>>>>

The challenge of making decisions under uncertainty is not unique to fisheries. Optimal control-based decision methods which assume perfect measurements are applied to a wide range of population and ecosystem management issues, including fire ecology [@Richards1999], invasive species [@Blackwood2010; @Shea1998], disease outbreaks [@Shea2014; @Li2017], and protecting biodiversity [@Dee2017; @Iacona2017], and in common textbooks and reviews [@Mangel1985; @Clark1990; @Marescot2013].  Yet fisheries conservation and management has long been both a crucible and proving ground for the theory of ecological management more generally, including topics such as adaptive management [@Walters1978], ecosystem-based management [@Levin2008] and resilience thinking [@Holling1973; @May1977], while also giving rise to the sub-discipline of resource economics [@Beverton1957; @Schaefer1954; @Gordon1954], thanks to its global relevance, long history, and readily available data.  Despite the generality of the models and issue of measurement uncertainty considered here, any application must be grounded in both the history and context of the particular decision problem. In light of this, we begin with a brief background on existing decision theory approaches common in fisheries management.

In this paper, we examine three strategies to managing a natural population, such as a fishery, under such uncertainty.  This problem has a long history in both theory and practice, where seemingly innocuous simplifying assumptions have led to a deep paradox in how managers should respond to uncertainty.  The precautionary principle [@Kriebel2001] would seem to suggest that the greater the uncertainty in our models, the more cautious we should be in management policies.  Yet a well-known mathematical proof by @Reed1979 established that under quite general conditions, the optimal strategy under uncertainty is no different than under no uncertainty at all.  Attempts to resolve this have since only deepened this paradox, arguing that adding additional sources of uncertainty, such as imperfect measurements, should lead to optimal harvest that increases with greater uncertainty [e.g. @Clark1986; @Sethi2005].  Meanwhile, much of actual practice has (perhaps fortunately, as we shall see) ignored these results in favor of a more heuristic application of the precautionary principle.  Here, we show that this paradox can be resolved by uncovering previous shortcuts and tackling the optimal management problem head-on, which we can solve thanks to the computational efficiency of sophisticated algorithms developed more recently in the field of robotics.  This approach allows us to reject this paradox largely in favor of the precautionary principle. Further, our comparisons show that widely recognized existing approaches in both theory and practice are not by themselves sufficient to manage a population under substantial uncertainty over the long term, but our recently borrowed approach from robotics literature can under identical conditions sustain both higher biomass and higher economic yields than those approaches.  This conclusion has important implications not only for fisheries but ecosystem more broadly: First, our results highlight that measurement error must be accounted for in both the decision process itself, and not merely in the estimation of model. Second, these results underscore the opportunity to learn from engineering fields such as robotics when faced with complex and uncertain decisions that we have previously dismissed as intractable.

@@

where the $\min$ function ensures no additional reward for attempting to harvest more than the entire stock.  In economic terms, this corresponds to a fixed price per fish caught, with no proportional cost on effort required to do so, but the results do not depend on this assumption, as existing analyses have previously established [@Reed1979].  Using this form allows a more direct comparison to approaches such as maximum sustainable yield (MSY) which do not include an economic model but merely maximize long-term catch. In principle, utility could also reflect ecosystem services or other intrinsic values for fish left in the sea and not merely the market for consumption [@Halpern2013].

The solution to this decision problem is conditional on a population model for the underlying ecological process, describing the probability that the system moves to state $x_{t+1}$ given that it was in state $x_t$ and the manager selected a harvest $h_t$, which we discuss below.  Such a model would typically be estimated and parameterized from available data, often (but not necessarily) using a hierarchical Bayesian approach that acknowledges the existence of uncertainty in both measurements and process [e.g. see @Dichmont2016 for a discussion of how uncertainties are frequently included in stock assessment models].  However, accounting for measurement uncertainty when going from data to model does not mean we have also accounted for this uncertainty when going from model to decision.  For example, a harvest decision policy based upon maximum sustainable yield simply depends on the stock size which maximizes the expected growth rate of the model.  Measurement uncertainty in model estimation can indeed influence the position of that maximum, but as we shall see, that strategy is only optimal in the absence of any uncertainty.

There is one further subtlety arising in this seemingly simple problem statement that we must address. Given our discrete-time formulation of the recruitment process, it is necessary to decide if the measurement $y_t$ happens before or after harvest $h_t$: that is do we: measure, recruit, harvest, or measure, harvest, recruit?  Following convention in the optimal control literature [e.g. @Reed1979; @Clark1990; @Sethi2005], we will assume the latter; measurement occurs immediately before harvest, followed by recruitment. This assumption has occasionally been reversed to introduce some additional uncertainty from stochastic recruitment immediately prior to setting the harvest quota [e.g. @Clark1986; @Weitzman2002], which appears to mimic uncertainty in measurements but does not allow uncertainty to accumulate since the measurement step still occurs without error.

@@

@Gordon1954 and @Schaefer1954 independently showed that the maximum sustainable yield is achieved by reducing the stock to the population to the size at which it obtains the maximum growth rate.  This stock size is known as Biomass at Maximum Sustainable Yield, $B_{MSY}$. For the Gordon-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$.  They observed that fishing at a *constant yield* (that is, an individual fish mortality, $F$, such that harvest $H = F \cdot B$) of $F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}$)  will eventually lead to a population that converges to the biomass $B_{MSY}$ and produces the maximum sustainable harvest, $H_{MSY} = r K / 4$ in this model.  From here, theory and practice diverge.

@@

In the face of a naturally fluctuating population, previous arguments made by @Gordon1954; @Schaefer1954 or @Clark1973 no longer hold.  As noted above, the optimal harvest of a population under a model such as the stochastic Gordon Schaefer, Eq \eqref{Gordon-Schaefer}, is an example of a Markov Decision Problem (MDP) which must be solved with stochastic dynamic programming. Thanks to a mathematical proof provided by @Reed1979, fisheries managers have largely been able to bi-pass such computational effort.  However, this convenient result also opened the door to paradox of uncertainty that has persisted in ecological management for the past four decades.

@@

Algorithmic innovations from the robotics community have now made it possible to numerically solve non-trivial POMDP problems. The need to consider all past observations becomes particularly demanding given the forward-looking nature of a decision problem.  Not only must we consider all possible sequences of future actions over all possible sequences of future states, but we must add to that all possible sequences of future measurements. The computational complexity involved has historically limited POMDP applications to contexts with only a handful of possible states and actions [e.g. @Chades2008; @Chades2011; @Fackler2014; @Fackler2014b], insufficient to capture fisheries models appropriately.  Meanwhile, methods to solve decision problems with imperfect information have advanced steadily in the field of robotics and artificial intelligence.  Almost contemporaneous with Reed's work,  papers by @Smallwood1973 and @Sondik1978 laid mathematical foundations for algorithms that could efficiently solve POMDP problems [e.g. @Kaelbling1998; @Pineau2003].  More recently, driven by demands in areas such as autonomous vehicle decision making, newer point-based approximation algorithms such as SARSOP [@Kurniawati2008] have made it possible to solve POMDPs with 100s of states and actions.  We have adapted this algorithm for application to the fisheries context, and provide an efficient implementation as a preliminary R package [@sarsop-pkg] which can be used to replicate and further explore results presented here. Details of the analysis presented here including annotated code to reproduce and further explore all of the following results are provided in the supplementary material.

Precise definitions of both the (fully observed) MDPs and POMDPs (not to be confused with Markov Process Models and Hidden Markov Process Models -- methods for which estimate the model but do not involve the feedback of any decision process) in an ecological context can be found in @Williams2011, or in classic work from the engineering and robotics community [e.g. @Smallwood1973; @Sondik1978].  For convenience, we summarize the POMDP definition and common notation here.  The POMDP problem is posed identically to that of the MDP problem, with the addition of an observation process  The POMDP problem for fisheries question considered here can be summarized as follows:

- Transition process (state equation): $T(x_t, x_{t+1}, a_t)$: the probability that a system is in state $x_{t+1}$ at time $t+1$ given that it began in state $x_t$ at time $t$ and the manager took action $a_t$.  In our context, this relationship is given by the Gordon-Schaefer stock recruitment function $f$ with normally distributed growth uncertainty $x_{t+1} \sim \mathcal{N}(f(x_t,a_t), \sigma_g)$, truncated at zero to exclude negative population sizes. The action $a_t$ represents the harvest quota set for the fishery. Attempting to implement a quota the exceeds the true population size results in collapse of the fishery.  As @Clark1986 eloquently argues, assuming that extinction is impossible regardless of fishing intensity would unreasonably bias the decision problem.

@@

fig1_df %>% 
  mutate(ymax = mean + sd, ymin = pmax(mean - sd, 0)) %>%
  ggplot(aes(time, mean, col = method, fill = method)) + 
  geom_line(lwd=1) + 
  geom_ribbon(aes(ymax = ymax, ymin = ymin), col = NA, alpha = 0.1) +
  facet_wrap(~ sigma_m, labeller = label_bquote(sigma[m] == .(sigma_m))) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

In the absence of either environmental noise or measurement error POMDP, CE, and MSY would converge to stock at the $B_{MSY}$, while TAC would maintain the stock at a slightly higher level (see Supplemental material, Figure S1).  The introduction of stochastic growth has a significant negative impact on the TAC strategy, with a mean biomass significantly lower than $B_{MSY}$ (first panel, Figure \ref{sims}; this impact is even more severe for MSY, see Figure S2).  Without measurement error, the CE and POMDP strategies are nearly identical with both approximately maintaining the stock at $B_{MSY}$ despite the significant environmental stochasticity.  As measurement error increases in the subsequent panels, CE and TAC strategies perform increasingly poorly, while the POMDP continues to maintain the average stock close to $B_{MSY}$.  Notably, CE is significantly more impacted by measurement uncertainty than TAC, with CE averaging even lower biomass than TAC under moderate measurement uncertainty.  These results confirm that the precautionary approach represented by the TAC does indeed prove more robust to the problem of measurement error than the optimization solution represented by CE, but is less robust to environmental error. Many of the replicate simulations under CE experience complete stock extinction under large measurement error, owing to the arbitrarily large harvests permitted by the "bang-bang" nature of the CE policy. In contrast, the POMDP approach successfully handles both sources of uncertainty, maintaining higher stocks, near $B_{MSY}$ level, and producing the highest yield.

```{r econ, fig.width=7, fig.height=3.5, fig.cap="Expected net present value of the fishery across strategies under increasing levels of measurement error $\\sigma_m$. Net present value is the sum of all future harvests discounted over time and averaged across 100 replicates simulations under each strategy, assuming discount factor $\gamma = 0.95$, as shown in Figure \\ref{sims}. The value under constant escapement (CE) is optimal when measurements are perfect but decreases rapidly with increasing measurement error. The more cautious TAC is not economically optimal but largely unimpacted by increasing error, while POMDP attains consistently high economic yield despite the increasing uncertainty. \\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "MSY") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

@@

This pattern in management success in ecological terms (the relatively recovery and maintenance of fish biomass) is also borne out in terms of economic performance. We find the mean net present value (averaging across replicates and discounting future profits by the discount factor $\gamma = 0.95$) for these same simulations at increasing levels of measurement uncertainty (Figure \ref{econ}).  As before, environmental stochasticity is set at $\sigma_g = 0.15$.  In the absence of measurement uncertainty, constant escapement (CE) is optimal (as per @Reed1979), while the heuristic caution built into the total allowable catch (TAC) strategy (at 80% MSY) results in a sub-optimal economic yield.  The presence of stochasticity in recruitment ($\sigma_g = 0.15$), also contributes to the reduction in yield under TAC.  Though CE is quite robust to the environmental stochasticity level, this strategy proves very sensitive to increasing measurement error, showing sharp declines in economic value, falling below the TAC economic value at $\sigma_m = 0.15$.    Though the risk of stock collapse does increase with increasing measurement error under TAC (as seen by the mean declines in Figure \ref{sims}), these have little impact on the economic value due to the discount rate.  A smaller discount rate would penalize unlikely but not improbable collapses more, since a significant amount of time is required to realize those rare events.  Supplemental Figure S3 summarizes these economic trends across different noise values $\sigma_g$ and includes comparison to a simple MSY policy.  In contrast to the declining economic performance of CE and the consistently sub-optimal economic yield for TAC, the POMDP strategy continues to generate economic yields at approximately the optimal level (as attained by CE in the absence of measurement error) despite the increasingly uncertain measurements.  This demonstrates that the reduced risk of stock collapse and higher average stock biomass attained by the POMDP strategy in the presence of high measurement error, Figure \ref{sims} is not the result of a trivial reduction in harvesting under all circumstances, but rather, evidence of a more nuanced strategy that manages to account for the uncertainty in measurement while maintaining a reasonable harvest.

@@

```{r overest, fig.width=4, fig.height=3.5, fig.cap = "Average fish biomass when the POMDP strategy assumes a high level of measurement uncertainty, while simulations reflect perfect measurements.  Despite this overestimation, biomass under POMDP strategy closely tracks the optimal biomass under CE in the absence of measurement error.  Solid lines indicate averages over 100 simulations, colored bands indicate +/- one standard deviation. \\label{overest}"}
overest_sims %>%
  filter(method != "MSY") %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = pmax(mean-sd,0)), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))  + 
  theme(legend.position = "bottom") 
```

@@

This difference between underestimating and overestimating accounts for the poor performance of the CE solution under large measurement uncertainty, where it over-harvests whenever measurements are too large.  Even though underestimating is equally likely under the measurement uncertainty model, sooner or later a run of "heads", a sequence of overestimations relative to the true stock, can drive stocks to very low levels where the chance of stock extinction becomes possible.  It is precisely this asymmetry: that too much over-harvesting leads to an irreversible state of extinction, while too much under-harvesting is always reversible (modulo some lost revenue) that lay behind Clark's original intuition that there was something fishy about Reed's result that $S = D$: that uncertainty required no extra caution.  Constant escapement is particularly susceptible to over-harvesting starting from stock sizes much higher than $B_{MSY}$ since its bang-bang optimal solution attempts to bring stocks back to target level as fast as possible. CE is not so vulnerable to collapse from small stock sizes, since it shuts down all harvests once estimates fall below $B_{MSY}$. Stock collapse under TAC can also be driven by such a string of heads, but is unlikely at high stock sizes since harvest never exceeds $H_{MSY}$.  In both cases, some measurement uncertainty interacts with inherent stochasticity, which provides a continued source of variation to sizes above $B_{MSY}$, where CE strategy is most vulnerable, and below $B_{MSY}$, where TAC is most vulnerable.

@@

Using modern algorithms we have been able to both crack the nut of measurement uncertainty in the optimal management of ecological populations such as marine fisheries, debunking a long-standing paradox created by previous literature which has argued that increased measurement uncertainty should be met with equal or larger harvests [e.g. @Reed1979; @Clark1986; @Sethi2005].  By using powerful algorithms developed first in the robotics literature to solve POMDPs [@Kurniawati2008], we have been able to tackle this optimal control problem directly rather than resorting to the simplifying assumptions used in previous work.  Our solution confirms the intuition of the precautionary principle in a quantitatively precise form: under most (but not all) conditions, *greater uncertainty results in smaller optimal harvests*.  Despite frequently proposing smaller harvests than existing approaches, the POMDP solution achieves higher long-term economic value as well as higher average stock sizes over the long term.

### 2018-11-22 reviews/README.Rmd
minor edits on 2nd review

---
title: "README.Rmd"
author: "Carl Boettiger"
date: "12/13/2017"
output: github_document
---

@@

>>>>

---
title: "README.Rmd"
author: "Carl Boettiger"
output: github_document
---

@@

Encrypt letter 3

```{r}
letter3 <- "review-reply-3.Rmd"
gpg_letter3 <- "review-reply-3.Rmd.gpg"

msg <- gpg_encrypt(letter3, receiver = cboettig, signer = cboettig)
writeLines(msg, gpg_letter3)
```

```{r}
writeLines(gpg_decrypt(gpg_letter3), letter3)
```
